Experiences in teaching with Jupyter with nbgrader

### 2019-09-24 paper/paper.tex
some ideas added to the introduction

Your text comes here. Separate text sections with

\section{Section title}
\label{sec:1}
We discuss Jupyter \cite{jupyter-edu-book} and nbgrader \cite{nbgrader}.

@@

% Non-BibTeX users please use
\begin{thebibliography}{99}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{jupyter-edu-book}
Barba, L. A., Barker, L. J., Blank, D. S., Brown, J, Downey, A. B., George, T.,
Heagy, L. J., Mandli, K. T., Moore, J. K., Lippert, D., Niemeyer, K. E.,
Watkins, R. R., West, R. H., Wickes, E., Willing, C., \& Zingale M. (2019).
Teaching and Learning with Jupyter,
\url{https://jupyter4edu.github.io/jupyter-edu-book/}.
\bibitem{nbgrader}
% https://doi.org/10.21105/jose.00032 
Project Jupyter, Blank, D., Bourgin, D., Brown, A., Bussonnier, M.,
Frederic, J., Granger, B., Griffiths, T. L.,  Hamrick, J., Kelley, K.,
Pacer, M., Page, L., P{\'e}rez, F., Ragan-Kelley, B., Suchow, J. W.,
\& Willing, C. (2019).
nbgrader: A Tool for Creating and Grading Assignments in the Jupyter Notebook,
\textit{Journal of Open Source Education}, 2(11), 32.
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

>>>>

In recent years, Python has become increasingly popular as a first programming
language at universities. Due to its expressive code, it provides a low entry
barrier for students while at the same time being well suited for serious
scientific work (for prominent recent examples see \cite{gw150914} and
\cite{EHT}). In a teaching environment, the availability of a Python
distribution for all operating systems likely to be used by students proves to
be very helpful to ensure a consistent working environment for all students.

The development of the Jupyter notebook has opened up exciting new
possibilities in teaching \cite{jupyter-edu-book}. At the same time,
the Jupyter notebook has become the de facto standard among data
scientists. Employing the Jupyter notebook in teaching provides the
students not only with new way to learn but also with a tool potentially
useful for their further career.

While it is possible to run the Jupyter notebook with a Python kernel on the
students' computer, the fact that work with the Jupyter notebook is browser-based
suggests to provide students with an access to a Python kernel via a Jupyterhub.
This approach avoids any installation requirements on the students' side besides
the availablility of a browser.

For the Jupyter notebook, the extension \texttt{nbgrader} was developed
\cite{nbgrader} which serves as a tool to distribute, collect and grade problem
sets for exercises. In the most recent version (0.6.0) at the time of this
writing, the possibility of giving feedback to students has been significantly
facilitated.

\section{Section title}
\label{sec:1}

@@

% Non-BibTeX users please use
\begin{thebibliography}{99}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{gw150914}
% https://doi.org/10.1103/PhysRevD.93.122003
Abbott, B. P. \textit{et al.} (2016).
GW150914: First results from the search for binary black hole coalescence with Advanced LIGO,
\textit{Physical Review D}, 93(12), 122003.

\bibitem{EHT}
% https://doi.org/10.3847/2041-8213/ab0c57
The Event Horizon Telescope Collaboration (2019).
First M87 Event Horizon Telescope Results. III. Data Processing and Calibration,
\textit{The Astrophysical Journal Letters} 875(1), L3.

\bibitem{jupyter-edu-book}
Barba, L. A., Barker, L. J., Blank, D. S., Brown, J, Downey, A. B., George, T.,
Heagy, L. J., Mandli, K. T., Moore, J. K., Lippert, D., Niemeyer, K. E.,
Watkins, R. R., West, R. H., Wickes, E., Willing, C., \& Zingale M. (2019).
Teaching and Learning with Jupyter,
\url{https://jupyter4edu.github.io/jupyter-edu-book/}.

\bibitem{nbgrader}
% https://doi.org/10.21105/jose.00032 
Project Jupyter, Blank, D., Bourgin, D., Brown, A., Bussonnier, M.,
Frederic, J., Granger, B., Griffiths, T. L.,  Hamrick, J., Kelley, K.,
Pacer, M., Page, L., P{\'e}rez, F., Ragan-Kelley, B., Suchow, J. W.,
\& Willing, C. (2019).
nbgrader: A Tool for Creating and Grading Assignments in the Jupyter Notebook,
\textit{Journal of Open Source Education}, 2(11), 32.
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
